Loop-Aware Optimizations in PyPy's Tracing JIT

### 2011-06-16 talk/iwtc11/paper.tex
start describing benchmarks

XXX we need Psyco numbers

>>>>

Benchmarks were run on Intel i7 M620 @2.67GHz with 4M cache and 8G of RAM in
32bit mode.
The machine was otherwise unoccupied. We run the following software
for benchmarks:

\begin{itemize}
\item PyPy 1.5
\item CPython 2.7.2
\item Psyco 1.6 with CPython 2.6.6
\item GCC 4.4.5 shipped with Ubuntu 11.4
\end{itemize}

We run GCC both with -O2 optimization and -O3 -march=native, disabling the
automatic loop vectorization. In all cases, SSE2 instructions were used for
floating point operations, except Psyco which uses x87 FPU instructions.
We also run PyPy with loop peeling optimization and without (but otherwise
identical).

XXX discuss some more, explain why gcc is faster
XXX we need Psyco numbers
